Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2016-01-19 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
increase tolerance on slanted cell meshes to 2dz/5

Cut cell grids are generated in a different way to the typical shaving technique described by \citet{adcroft1997}.  Starting from a uniform grid, all cell vertices that lie beneath the orography are moved up to the surface.  Additionally, to avoid creating very thin cells, all vertices up to $\Delta z/5$ above the orography are moved down to the surface.
Where all four of a cell's vertices are moved, the cell has zero volume and so it is removed.  Where two vertices at the same horizontal location are moved up to the surface they will occupy the same point; this results in a zero-length edge that is removed to create a triangular cell.  Figure~\ref{fig:grid-generation} shows how a $2 \times 2$-cell, uniform grid is transformed into a cut cell grid.  Cell $c_4$ is removed because it has zero volume, and the zero-length edge at point $p$ is removed to create a triangular cell, $c_3$.

@@

\begin{figure*}
	\centering
	\includegraphics{../fig-grid-generation/fig-grid-generation.pdf}
	%
	\caption{Illustration of a slanted cell grid (a) before, and (b) after construction.
	The terrain surface, denoted by a heavy dotted line, intersects a uniform rectangular grid comprising six cells, $c_1, \ldots, c_6$.  The cell vertices, marked by open circles, are moved to the points at which the terrain intersects vertical cell edges, marked by filled circles.  Cells that have no volume are removed.  Where a cell has two vertices occupying the same point, the zero-length edge that joins those vertices is removed.  In this illustration, cells $c_5$ and $c_6$ are removed because they have no volume, and the zero-length edge at point $q$ is removed to create a triangular cell, $c_4$.  Point $p$ is moved down because it is within $\Delta z/5$ of the surface, avoiding the creation of a thin cell.}
	\label{fig:grid-generation}
\end{figure*}

>>>>

Cut cell grids are generated in a different way to the typical shaving technique described by \citet{adcroft1997}.  Starting from a uniform grid, all cell vertices that lie beneath the orography are moved up to the surface.  Additionally, to avoid creating very thin cells, all vertices up to $2 \Delta z/5$ above the orography are moved down to the surface.
Where all four of a cell's vertices are moved, the cell has zero volume and so it is removed.  Where two vertices at the same horizontal location are moved up to the surface they will occupy the same point; this results in a zero-length edge that is removed to create a triangular cell.  Figure~\ref{fig:grid-generation} shows how a $2 \times 2$-cell, uniform grid is transformed into a cut cell grid.  Cell $c_4$ is removed because it has zero volume, and the zero-length edge at point $p$ is removed to create a triangular cell, $c_3$.

@@

\begin{figure*}
	\centering
	\includegraphics{../fig-grid-generation/fig-grid-generation.pdf}
	%
	\caption{Illustration of a slanted cell grid (a) before, and (b) after construction.
	The terrain surface, denoted by a heavy dotted line, intersects a uniform rectangular grid comprising six cells, $c_1, \ldots, c_6$.  The cell vertices, marked by open circles, are moved to the points at which the terrain intersects vertical cell edges, marked by filled circles.  Cells that have no volume are removed.  Where a cell has two vertices occupying the same point, the zero-length edge that joins those vertices is removed.  In this illustration, cells $c_5$ and $c_6$ are removed because they have no volume, and the zero-length edge at point $q$ is removed to create a triangular cell, $c_4$.  Point $p$ is moved down because it is within $2 \Delta z/5$ of the surface, avoiding the creation of a thin cell.}
	\label{fig:grid-generation}
\end{figure*}
